\addcontentsline{toc}{section}{\hspace{17pt}Abstract} % Adds to the Table of contents
\section*{Abstract}

\textbf{TODO:}\\
\textbf{An academic abstract typically outlines four elements relevant to the completed work:}

    \textbf{- The research focus (i.e. statement of the problem(s)/research issue(s) addressed);}\\
    \textbf{- The research methods used (experimental research, case studies, questionnaires, etc.);}\\
    \textbf{- The results/findings of the research; and}\\
    \textbf{ - The main conclusions and recommendations}
    
\textbf{Improve/cut down on the following:}

This paper is about our collaboration with a group of students from the Singapore Management University and our experiences gained from that collaboration. We encountered planning issues due to time difference, cultural differences and language barriers.

Doing our collaboration, we were to produce web services to be consumed by clients respectively written by us and the group from Singapore. Both clients would be websites allowing purchases and/or rentals of various media.
Based on our use cases and the use cases of the Singaporean group we produced an extensive web service interface, which was approved by the Singaporean group.

We chose to write the web service with a F\Sh backend. This was a new language to us, but it turned out to be an amazing language with many strong features and we do not regret our choice.
At our agreed upon deadline our code was lacking proper testing, and we had some long evenings, correcting our errors as the Singaporeans reported them.

The final server ended up being very fast - a lot faster than we had anticipated. It did lack some essential features though, and this made some of the features of our client harder to implement.

After two months our collaboration with the Singaporean group came to an end and it was time for us to write our own client. We chose to write it in Object Oriented PHP. Some of us had previous experience with this language, and we all wanted to try it out. We planned our client thoroughly and ended up using a lot of clever patterns. The final system is very extendable and maintainable.

Our client ended up being quite good, even though we did not meet all our requirements. We had very little time left at the end of the project, and some functionality had to be cut.
\newpage