\subsubsection{Requirements}
\label{s_serviceRequirements}
This section will focus on the requirements for the server. The following list, lists the non-functional requirements we have set for the web service.
\\
\begin{enumerate}[label=NFR-\arabic*]
	\item When put into production the server should have an uptime of at least 99 \% of planned uptime. Downtime, due to maintenance, must be announced at least 48 hours ahead.
	\item From the time a request has been received, to the time an answer has been sent, no more than 500 millisecond must have passed. Expect when the answer contains a product-file (image, movie, video, etc.), in this case there is no deadline.
	\item All data (except the product-file itself) must be persisted for at least 5 years after it has gone out of usage (for legal reasons).
\end{enumerate}

From the use case diagram and the use cases we have produced a list of functional requirements to the web service.

\begin{enumerate}[label=FR-\arabic*]
	\item Register new account
	\item Log in
	\item Log out
	\item Customers can buy products
	\item Customers can rent products
	\item Customers can rate products
	\item Customers can stream products
	\item Customers can download products
	\item Customers and content providers can change their own account information
	\item Content providers can upload product files
	\item Content providers can create new products
	\item Content providers can upload product thumbnails
	\item Content providers can change informations about their own products
	\item Admins can change information about any product
	\item Admins can change information about any account
	\item Admins can get a list of all accounts
	\item Admins can ban an account
	\item Admins can unban an account
\end{enumerate}