\subsection{Conclusion}
\label{serverconclusion}
In the requirements section, we list three non-functional requirements. Due to the combined load on the shared server our uptime and response time requirements have not always been met.

We meet almost all requirements, but we are lacking the following functionality:
\begin{itemize}
\item Handling of metadata
\item Deletion of products
\item Acquiring the last authentication time of an account
\end{itemize}

In this part of the project we collaborated with a group of students from Singapore. The collaboration went very well. Collaboration over such a great distance and through time zones was not always optimal, and communication multiple times a week was crucial.
Collaborating with another group gave us a different perspective upon many things and their input was appreciated. It was also helpful to us to have them use our service and inform us about any bugs we missed.
The collaboration also forced us to write a flexible service since we did not want to limit their client with a narrow designed web services. \textbf{[TODO: wat?(Mo)]}

We wrote our server primarily in F\Sh. It was supposed to have a thin layer of C\Sh for the web services, but that layer got more responsibility than intended. 
F\Sh was a new language to all of us and now that we have more experience with the language we would have done a lot of things differently. Finding errors in our code can be quite troublesome and unfortunately we did not find the time to implement logging functionality. We like the language very much and all of us would like to use the language, or a similar one, again sometime. We also get the impression that our services run very fast though we did not write the code with performance in mind.
\newpage