\subsubsection{Known Bugs}
From the first release of our server we have held a list of known bugs and a list of things yet not implemented. These were kept assure throughout the development process. \todo{What?}{Morten}
\\Here are the lists showing the current shortcomings of our server:
\subsubsubsection{Bug list}
\begin{itemize}
\item Adding metadata to products does not work.
\item Description string for products cannot pass more than 80 characters.
\item Deleting products not implemented.
\end{itemize}
The problem with the length of the description string, is a problem with our JSON serializer and should not take long to correct.
\subsubsubsection{To do}
\begin{itemize}
\item Handling metadata implemented, but not made available.
\item Somehow support deletion of products without robbing the customer of his purchase.
\item Correct product rating calculations.
\item Correct the improper detection of data too large to be handled by the database.
\item Implement ControlledProduct and ControlledCredits properly.
\end{itemize}
\subsubsubsection{Improvements}
While writing our client we discovered a number of things our server does not support which would have made it easier to write the client. There are also a couple of things we simply did not prioritize when we wrote the server.
\begin{itemize}
\item Encryption and security in general.
\item Simple web service methods such as a more specified method to get one or a few products.
\item A method for getting unpublished products for the Content Providers Dashboard.
\item Being able to limit the number of items returned from a service call.
\end{itemize}
\todo{More?}{Claus}